The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
Some formatting for guard compilation figure

\todo{Figure needs better formatting}
\begin{figure}[ht]
  \noindent
  \centering
  \begin{minipage}{1\columnwidth}
\begin{lstlisting}[mathescape, numbers=right, escapechar=|, firstnumber=18]
$b_3$ = int_eq($i_5$, 1)                    |\setcounter{lstnumber}{17}|
guard_false($b_3$)                          |\setcounter{lstnumber}{-1}|
\end{lstlisting}
  \end{minipage}
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
MOVEQ r8, #1
MOVNE r8, #0
CMP r8, #0
BEQ <bailout>
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
BNE <bailout>
...
...
...
    \end{lstlisting}
  \end{minipage}
  \caption{Result of separated (left) and merged (right) compilation of operations and guards (top).}
  \label{fig:trace-compiled}
\end{figure}

>>>>

%\todo{Figure needs better formatting}
\begin{figure}[ht]
  \noindent
  \centering
  \begin{minipage}{1\columnwidth}
\begin{lstlisting}[xleftmargin=20pt,xrightmargin=20pt,framexleftmargin=5pt,framexrightmargin=-10pt,mathescape, numbers=right, escapechar=|, firstnumber=18,frame=b]
$b_3$ = int_eq($i_5$, 1)                    |\setcounter{lstnumber}{17}|
guard_false($b_3$)                          |\setcounter{lstnumber}{-1}|
\end{lstlisting}
  \end{minipage}
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
MOVEQ r8, #1
MOVNE r8, #0
CMP r8, #0
BEQ <bailout>
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
BNE <bailout>
...
...
...
    \end{lstlisting}
  \end{minipage}
  \caption{Result of separated (left) and merged (right) compilation of one guard and the following operation (top).}
  \label{fig:trace-compiled}
\end{figure}
